\begin{fullwidth}
\section{Executive Summary}

The CARE Lab Fraud Fighters Team continued efforts to assist Sam with her hiring process and determining the legitimacy of her offer. During the second day of the engagement, the team met with Sam to provide guidance throughout a text-based job interview conducted on Microsoft Teams. There were a number of red flags encountered during the interview as well as discrepancies between the information provided within the interview and the initial email. The most notable of these discrepancies was that Mr. David W. Bondeson did not conduct the interview as previously mentioned and that the company Omnicell, Inc was used interchangeably with HealthComp, LLC despite no relation.\\\medskip

Afterwards, the team sat in on a follow up text based meeting with Sam during which she received a job offer email from the prospective employer/scammer. This email contained several red flags potentially indicating it as a phishing email. As part of the on boarding process Sam was asked to fill out a job application form, W4, and provide a passport photo.\\\medskip

The team has compiled a comprehensive report detailing OSINT findings, potential red flags, a comprehensive timeline with MITRE ATT\&CK Mappings, NIST Phish Scale evaluations of Sam's emails, as well as a to-do list and game plan for Sam moving forward. The compiled evidence indicates that this employment opportunity is extremely likely to be a scam; the team has prepared a comprehensive brief to communicate the red flags, and risks of moving forward to Sam.
\end{fullwidth}